Working with bibliography in texor

### 2023-07-24 supplement/bibliography/rebib.tex
Updated Supplementary material for rebib

\begin{Schunk}

\textbf{Setup :}
\begin{Sinput}
dir.create(your_article_folder <- file.path(tempdir(), "exampledir"))
example_files <-  system.file("article", package = "rebib")
x <- file.copy(from = example_files,to=your_article_folder,recursive = T)
your_article_path <- paste(your_article_folder,"article",sep="/")
\end{Sinput}
\end{Schunk}

\begin{Schunk}

\textbf{Input :}
\begin{Sinput}
file_name <- rebib:::get_texfile_name(your_article_path)
bib_items <- rebib:::extract_embeded_bib_items(your_article_path,file_name)
bib_items[[1]]
\end{Sinput}

\textbf{Output :}
\begin{Soutput}
#> [1] "\\bibitem[Ihaka, Ross and Gentleman, Robert]{ihaka:1996}"                          
#> [2] "Ihaka, Ross and Gentleman, Robert"                                                 
#> [3] "\\newblock \\emph{R: A Language for Data Analysis and Graphics.}"                  
#> [4] "\\newblock \\emph{Journal of Computational and Graphical Statistics}, 3:\\penalty0"
#> [5] "299--314, 1996."                                                                   
#> [6] "\\newblock URL : \\url{https://doi.org/10.1080/10618600.1996.10474713}"
\end{Soutput}
\end{Schunk}

@@

The first value to be parsed is the \verb|unique_id| also called the citation reference which is used to cite elements inside the article. Usually, this is in the first or second line of the whole entry. The position of the 
\verb|unique_id| will determine the position of the author names.
\begin{Schunk}

\textbf{Input :}
\begin{Sinput}
bib_items[[1]][1]
\end{Sinput}

\textbf{Output :}
\begin{Soutput}
#> [1] "\\bibitem[Ihaka, Ross and Gentleman, Robert]{ihaka:1996}"
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}

\textbf{Input :}
\begin{Sinput}
bib_items[[1]][2]
\end{Sinput}

\textbf{Output :}
\begin{Soutput}
#> [1] "Ihaka, Ross and Gentleman, Robert"
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}

\textbf{Input :}
\begin{Sinput}
bib_items[[1]][3]
\end{Sinput}
\textbf{Output :}
\begin{Soutput}
#> [1] "\\newblock \\emph{R: A Language for Data Analysis and Graphics.}"
\end{Soutput}
\end{Schunk}

This way the crucial elements of the bibliographic entry (unique_id, author names and title ) are parsed out.
The remaining data is stored as \verb|journal| internally and \verb|publisher| when writing to a new BibTeX file.

\begin{Schunk}

\textbf{Input :}
\begin{Sinput}
bib_items[[1]][4:6]
\end{Sinput}

\textbf{Output :}
\begin{Soutput}
#> [1] "\\newblock \\emph{Journal of Computational and Graphical Statistics}, 3:\\penalty0"
#> [2] "299--314, 1996."                                                                   
#> [3] "\\newblock URL : \\url{https://doi.org/10.1080/10618600.1996.10474713}"
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}

\textbf{Input :}
\begin{Sinput}
bib_entry <- rebib:::bib_handler(bib_items)
bib_entry
\end{Sinput}

\textbf{Output :}
\begin{Soutput}
#> $book
#> $book[[1]]
#> $book[[1]]$unique_id
#> [1] "ihaka:1996"
#> 
#> $book[[1]]$author
#> [1] "Ihaka, Ross and Gentleman, Robert"
#> 
#> $book[[1]]$title
#> [1] "R: A Language for Data Analysis and Graphics"
#> 
#> $book[[1]]$journal
#> [1] "Journal of Computational and Graphical Statistics 3:   :"
#> 
#> $book[[1]]$year
#> [1] "1996"
#> 
#> $book[[1]]$URL
#> [1] "https://doi.org/10.1080/10618600.1996.10474713"
#> 
#> $book[[1]]$isbn
#> NULL
#> 
#> $book[[1]]$pages
#> [1] "299--314"
#> 
#> 
#> $book[[2]]
#> $book[[2]]$unique_id
#> [1] "R"
#> 
#> $book[[2]]$author
#> [1] "R Core Team"
#> 
#> $book[[2]]$title
#> [1] "R: A Language and Environment for Statistical Computing"
#> 
#> $book[[2]]$journal
#> [1] "R Foundation for Statistical Computing Vienna Austria    :"
#> 
#> $book[[2]]$year
#> [1] "2016"
#> 
#> $book[[2]]$URL
#> [1] "https://www.R-project.org/"
#> 
#> $book[[2]]$isbn
#> [1] "3-900051-07-0"
#> 
#> $book[[2]]$pages
#> NULL
\end{Soutput}
\end{Schunk}

@@

\textbf{Input :}
\begin{Sinput}
file_path <- paste0(your_article_path,"/",file_name)
bib_path <- paste0(your_article_path,"/example.bib")
\end{Sinput}
\end{Schunk}

\begin{Schunk}

\textbf{Input :}
\begin{Sinput}
rebib:::bibtex_writer(bib_entry,file_path)
cat(readLines(paste(your_article_path,"example.bib",sep="/")),sep = "\n")
\end{Sinput}

\textbf{Output :}
\begin{Soutput}
#> @book{ihaka:1996,
#> author = {{Ihaka, Ross and Gentleman, Robert}},
#> title = {{R: A Language for Data Analysis and Graphics}},
#> publisher = {Journal of Computational and Graphical Statistics 3:   :},
#> pages = {299--314},
#> year = {1996},
#> url = {https://doi.org/10.1080/10618600.1996.10474713}
#> }
#> @book{R,
#> author = {R {Core Team}},
#> title = {{R: A Language and Environment for Statistical Computing}},
#> publisher = {R Foundation for Statistical Computing Vienna Austria    :},
#> year = {2016},
#> url = {https://www.R-project.org/},
#> isbn = {3-900051-07-0}
#> }
\end{Soutput}
\end{Schunk}

@@

\section{General usage}

\section{Bibliography aggregation}

>>>>

\begin{Sinput}
dir.create(your_article_folder <- file.path(tempdir(), "exampledir"))
example_files <-  system.file("article", package = "rebib")
x <- file.copy(from = example_files,to=your_article_folder,recursive = T)
your_article_path <- paste(your_article_folder,"article",sep="/")
file_name <- rebib:::get_texfile_name(your_article_path)
bib_items <- rebib:::extract_embeded_bib_items(your_article_path,file_name)
bib_items[[1]]
#> [1] "\\bibitem[Ihaka, Ross and Gentleman, Robert]{ihaka:1996}"                          
#> [2] "Ihaka, Ross and Gentleman, Robert"                                                 
#> [3] "\\newblock \\emph{R: A Language for Data Analysis and Graphics.}"                  
#> [4] "\\newblock \\emph{Journal of Computational and Graphical Statistics}, 3:\\penalty0"
#> [5] "299--314, 1996."                                                                   
#> [6] "\\newblock URL : \\url{https://doi.org/10.1080/10618600.1996.10474713}"
\end{Sinput}

@@

The first value to be parsed is the \verb|unique_id| also called the citation reference which is used to cite elements inside the article. Usually, this is in the first or second line of the whole entry. The position of the 
\verb|unique_id| will determine the position of the author names.

\begin{Soutput}
bib_items[[1]][1]
#> [1] "\\bibitem[Ihaka, Ross and Gentleman, Robert]{ihaka:1996}"
\end{Soutput}

@@

\begin{Sinput}
bib_items[[1]][2]
#> [1] "Ihaka, Ross and Gentleman, Robert"
\end{Sinput}

@@

\begin{Sinput}
bib_items[[1]][3]
#> [1] "\\newblock \\emph{R: A Language for Data Analysis and Graphics.}"
\end{Sinput}

This way the crucial elements of the bibliographic entry (unique\_id, author names and title ) are parsed out.
The remaining data is stored as \verb|journal| internally and \verb|publisher| when writing to a new BibTeX file.

\begin{Sinput}
bib_items[[1]][4:6]
#> [1] "\\newblock \\emph{Journal of Computational and Graphical Statistics}, 3:\\penalty0"
#> [2] "299--314, 1996."                                                                   
#> [3] "\\newblock URL : \\url{https://doi.org/10.1080/10618600.1996.10474713}"
\end{Sinput}

@@

\begin{Schunk}
\begin{Soutput}
bib_entry <- rebib:::bib_handler(bib_items)
bib_entry
#> $book
#> $book[[1]]
#> $book[[1]]$unique_id
#> [1] "ihaka:1996"
#> 
#> $book[[1]]$author
#> [1] "Ihaka, Ross and Gentleman, Robert"
#> 
#> $book[[1]]$title
#> [1] "R: A Language for Data Analysis and Graphics"
#> 
#> $book[[1]]$journal
#> [1] "Journal of Computational and Graphical Statistics 3:   :"
#> 
#> $book[[1]]$year
#> [1] "1996"
#> 
#> $book[[1]]$URL
#> [1] "https://doi.org/10.1080/10618600.1996.10474713"
#> 
#> $book[[1]]$isbn
#> NULL
#> 
#> $book[[1]]$pages
#> [1] "299--314"
#> 
#> 
#> $book[[2]]
#> $book[[2]]$unique_id
#> [1] "R"
#> 
#> $book[[2]]$author
#> [1] "R Core Team"
#> 
#> $book[[2]]$title
#> [1] "R: A Language and Environment for Statistical Computing"
#> 
#> $book[[2]]$journal
#> [1] "R Foundation for Statistical Computing Vienna Austria    :"
#> 
#> $book[[2]]$year
#> [1] "2016"
#> 
#> $book[[2]]$URL
#> [1] "https://www.R-project.org/"
#> 
#> $book[[2]]$isbn
#> [1] "3-900051-07-0"
#> 
#> $book[[2]]$pages
#> NULL
\end{Soutput}
\end{Schunk}

@@

\begin{Sinput}
file_path <- paste0(your_article_path,"/",file_name)
bib_path <- paste0(your_article_path,"/example.bib")
rebib:::bibtex_writer(bib_entry,file_path)
cat(readLines(paste(your_article_path,"example.bib",sep="/")),sep = "\n")
#> @book{ihaka:1996,
#> author = {{Ihaka, Ross and Gentleman, Robert}},
#> title = {{R: A Language for Data Analysis and Graphics}},
#> publisher = {Journal of Computational and Graphical Statistics 3:   :},
#> pages = {299--314},
#> year = {1996},
#> url = {https://doi.org/10.1080/10618600.1996.10474713}
#> }
#> @book{R,
#> author = {R {Core Team}},
#> title = {{R: A Language and Environment for Statistical Computing}},
#> publisher = {R Foundation for Statistical Computing Vienna Austria    :},
#> year = {2016},
#> url = {https://www.R-project.org/},
#> isbn = {3-900051-07-0}
#> }
\end{Sinput}
\end{Schunk}

@@

\section{General usage}
In general to use \CRANpkg{rebib} package, it is quite easy with requiring only one function call.
\subsubsection{Using with RJournal article}
In bibliography construction mode, \CRANpkg{rebib} will check for existing BibTeX files and will convert the embedded bibliography only when there are no linked BibTeX files in the RJ article.
\begin{verbatim}
%% typically rebib will search for this line in the RJ article, 
%% not the RJwrapper file
\bibliography{example}
\end{verbatim}
If there is no linked BibTeX file, \CRANpkg{rebib} will begin its procedure of converting the embedded bibliography to BibTeX and then link it with the article file as well.
\begin{Schunk}
\begin{Sinput}
# for files without BibTeX source
rebib::handle_bibliography(your_article_path)
#> Warning in get_bib_file(article_dir, file_name): No Bib files found !
#> BibTeX file does not exist
#> will parse for bibliography
#> bibtex file created
cat(readLines(paste(your_article_path,"example.bib",sep="/")),sep = "\n")
#> @book{ihaka:1996,
#> author = {{Ihaka, Ross and Gentleman, Robert}},
#> title = {{R: A Language for Data Analysis and Graphics}},
#> publisher = {Journal of Computational and Graphical Statistics 3:   :},
#> pages = {299--314},
#> year = {1996},
#> url = {https://doi.org/10.1080/10618600.1996.10474713}
#> }
#> @book{R,
#> author = {R {Core Team}},
#> title = {{R: A Language and Environment for Statistical Computing}},
#> publisher = {R Foundation for Statistical Computing Vienna Austria    :},
#> year = {2016},
#> url = {https://www.R-project.org/},
#> isbn = {3-900051-07-0}
#> }
\end{Sinput}
\end{Schunk}

\subsubsection{Bibliography aggregation}

If you have a BibTeX file and it is missing some references then this mode can help you read the embedded bibliography and combine the two bibliographies in a single BibTeX file.
\begin{verbatim}
# for files with BibTeX source as well as embedded entries
rebib::aggregate_bibliography(your_article_path)
#> Found Bib file  example.bib
#> bibliography aggregation possible
#> Found Bib file  example.bib
#> aggregation delta : 2
#> BibTeX file aggregated
\end{verbatim}

\subsubsection{Using with any LaTeX/BBL file}
The bibliography converter will convert any LaTex or BBL file given as a path. This way, one can generate BibTeX from the embedded bibliography or BBL file.
\begin{verbatim}
rebib::biblio_converter(path_to_your_file)
#> working directory : /temp/Rtmpt6Qk0v/exampledir/standalone
#> bib entries : 6
#> Written BibTeX file : /temp/Rtmpt6Qk0v/exampledir/standalone/sample.bib
\end{verbatim}
